Towards a Neural Co-Processor Which Restores Dexterity After Stroke: Modeling a Proof-of-Concept

### 2021-11-21 paper/article.tex
Paper progress

\section{Discussion}
\label{sec:discussion}

@@

Clearly, we need to examine carefully what can and cannot be inferred from simulation studies
such as these. As in Dura-Bernal \cite{bernal.sim}, we note that our simulation differs
drastically from an organic brain, both in scale and structure. Today, predicting long-running
neural responses to stimulation remains a difficult problem, implying targeted neural control
is also difficult. Even moreso, identifying the neural correlates of complex task success
remains largely out of reach \cite{khanna.openloop}. What, then, does our simulation provide us?

Abstractly, the co-processor lends itself to any closed-loop neural stimulation problem
where a relevant stimulation model can be identified. There are many lower dimensional problems
today which we address with far simpler stimulation regimes than would be necessary for
e.g. remediating the symptoms of a stroke. For example, deep brain stimulators for
treating the symptoms of Parkinson's Disease can now be controlled in a closed loop
fashion to also minimize stimulation side-effects and maximize implant battery life.
TODO: citation. Our simulation clearly does not imply that our co-processor design can
translate immediately to stroke applications. However, it does demonstrate that our design
can adapt to long-running effects of stimulation, as well as to the non-stationarity of
the neural circuit to which it is applying the stimulation. These properties together
suggest it could be useful in lower dimensional problems where a stimulation model can
be estimated, and stimulation parameters can be tied to the target objective. TODO: more examples?

On the whole, the co-processor quickly improved task performance, but required orders of magnitude
more training examples to achieve its highest levels of performance. This training inefficiency remains
a problem...

\begin{itemize}
	\item Co-processors can be trained, and they can adapt to a difficult problem
	\item One central issue that still needs work is data/training efficiency
	\item Pitch a couple ideas to help solve it:
		\begin{itemize}
			\item Continuous retraining of EN, rather than throwing it away
			\item Retain recent data and reuse it during training
		\end{itemize}
	\item Toward in vivo application: example of lower dimensional problems this may help with
\end{itemize}

\subsection{Learning efficiency}
Learning efficiency is a key concern for our design. Due to limits on patient fatigue,
limited time, implant battery life, and other concerns, it is not plausible to expect
a learning algorithm to have access to unlimited amounts of training data. As a result,
it is necessary to make efficient use of the data we can acquire.

One clear advantage of our co-processor approach is that, as in Dura-Bernal \cite{bernal.sim},
we can train our stimulation agent to a great degree

\section{Conclusion}
...
\subsection{Future application}
(on a lower dimensional problem presumably)

>>>>

\section{Discussion and Future Work}
\label{sec:discussion}

@@

Clearly, we need to discuss carefully what can and cannot be inferred from simulation studies
such as these. As in Dura-Bernal \cite{bernal.sim}, we note that our simulation differs
drastically from an organic brain, both in scale and structure. Today, predicting long-running
neural responses to stimulation remains a difficult problem, implying targeted neural control
is also difficult. Even moreso, identifying the neural correlates of complex task success
remains largely out of reach \cite{khanna.openloop}. What, then, does our simulation provide us?

Abstractly, the co-processor lends itself to any closed-loop neural stimulation problem
where a relevant stimulation model can be identified. There are many lower dimensional problems
today which we address with far simpler stimulation regimes than would be necessary for
e.g. remediating the symptoms of a stroke. For example, deep brain stimulators for
treating the symptoms of Parkinson's Disease can now be controlled in a closed loop
fashion. That allows them to minimize stimulation side-effects and maximize implant
battery life, while also reducing the patient's primary symptoms. TODO: citation. Our
simulation does not imply that our co-processor design can translate immediately to
stroke applications. However, it does demonstrate that our design can adapt to
long-running effects of stimulation, as well as to the non-stationarity of the neural
circuit to which it is applying the stimulation. These properties together suggest it may be
useful in lower dimensional problems where a stimulation model can be estimated, and
stimulation parameters can be tied to the target objective. TODO: more examples?

On the whole, the co-processor quickly improved task performance, but required orders of
magnitude more training examples to achieve its highest levels of performance. Even
moderate amounts of recovery may be valuable to a user, but nevertheless we consider
training efficiency to remain a problem. Due to limits on patient fatigue, time, implant
battery life, and other concerns, it is not plausible to expect a learning algorithm
to have access to unlimited amounts of training data. As a result, it is necessary to
make efficient use of the data we can acquire. We believe there exist at least three
mitigations for that:

\begin{itemize}
	\item Retraining an existing EN, rather than regularly creating a new one. As
	      mentioned above, we encountered difficulty with this approach, but it remains
	      to be seen if this is a fundamental problem with our training method, rather
	      than a peculiarity of our simulation. Also, it remains unclear if a solution
	      for our simulation exists as well, which we've simply yet to identify. This
	      remains a future area of inquiry.
	\item Making better use of what data we acquire. In this initial simulation we do
	      not retain data beyond the present training epoch. In practice, we can likely
	      retain training data for some time window. Non-stationarity requires us to
	      regularly discard or discount data as it ages. However, in practice, training
	      epochs operate on the order of seconds, suggesting that data can be retained
	      and reused for a period of time. The `speed' of non-stationarity compared to
	      the co-processor's learning therefore must be an area of future research.
	\item Matching the dimensionality of the stimulation parameters and observation
	      data to the amount of available data. If one chooses a stimulation regime with
	      a small number of controllable parameters, where nevertheless task improvement
	      from the stimulation is possible, that allows for a simpler co-processor, which
	      may require less training data. We discuss this next.
\end{itemize}

TODO: future applications
